preliminary_regression

### 2021-12-11 preliminary_analysis.Rmd
graphics

reg3 <- felm(percent_turnout ~ treat_post | city + year_int, data = election_all3)
stargazer(reg3, type = 'text',
          title = c("Effects of a Catastrophic Event on Voter Turnout"),
          column.labels = c('Voter Turnout'),
          covariate.labels = c('Treatment Effect'),
          dep.var.labels = c(''))
```
# Swing

@@

reg4 <- felm(swing ~ treat_post | city + year_int, 
             data = election_all4)
stargazer(reg4, type = 'text')
```

@@

stargazer(reg5, reg6, type = 'text')
```

@@

reg1_1 <- felm(incumbent_vote_share ~ treat_post_kurdish | city + year_int, 
             data = dummies)
reg1_2 <- felm(incumbent_vote_share ~ event_earthquake | city + year_int, 
             data = dummies)
reg1_3 <- felm(incumbent_vote_share ~ treat_post_cyprus | city + year_int, 
             data = dummies)
reg1_4 <- felm(incumbent_vote_share ~ treat_post_refugee | city + year_int, 
             data = dummies)

stargazer(reg1_1, reg1_2, reg1_3, reg1_4, type = 'text')

@@

stargazer(reg5_1, reg5_2, reg5_3, reg5_4, type = 'text')
```

>>>>

reg3 <- felm(percent_turnout ~ treat_post | city + year_int + election_type, data = election_all3)
stargazer(reg3, type = 'latex',
          title = c("Effects of a Catastrophic Event on Voter Turnout"),
          column.labels = c('Voter Turnout'),
          covariate.labels = c('Treatment Effect'),
          dep.var.labels = c(''))
```
# Swing

@@

reg4 <- felm(swing ~ treat_post | city + year_int + election_type, 
             data = election_all4)
stargazer(reg4, type = 'latex',
          title = c("Effects of a Catastrophic Event on Change in Leadership"),
          column.labels = c('Dummy for Leadership Change'),
          covariate.labels = c('Treatment Effect'),
          dep.var.labels = c('')
          )
```

@@

stargazer(reg5, type = 'latex',
          title = c("Effects of a Catastrophic Event on Incumbent Vote Share"),
          column.labels = c('Incumbent Vote Share'),
          covariate.labels = c('Treatment Effect'),
          dep.var.labels = c(''),
          notes = c('Only elections with non-swing result are considered.'))
```

@@

reg1_1 <- felm(incumbent_vote_share ~ treat_post_kurdish | city + year_int + election_type, 
             data = dummies)
reg1_2 <- felm(incumbent_vote_share ~ event_earthquake | city + year_int+ election_type, 
             data = dummies)
reg1_3 <- felm(incumbent_vote_share ~ treat_post_cyprus | city + year_int+ election_type, 
             data = dummies)
reg1_4 <- felm(incumbent_vote_share ~ treat_post_refugee | city + year_int+ election_type, 
             data = dummies)

stargazer(reg1_1, reg1_2, reg1_3, reg1_4, type = 'latex',
          title = c("Effects of a Catastrophic Event on Incumbent Vote Share"),
          dep.var.labels = c('Incumbent Vote Share'),
          covariate.labels = c('Kurdish Armed Conflict', 'Marmara Earthquake',
                               'Cyprus Peace Operation', 'Syrian Refugees'),
          notes = c('Only elections with non-swing result are considered.'))

@@

stargazer(reg5_1, reg5_2, reg5_3, reg5_4, type = 'latex',
           title = c("Effects of a Catastrophic Event on Voter Turnout"),
           dep.var.labels = c('Voter Turnout'),
           covariate.labels = c('Kurdish Armed Conflict', 'Marmara Earthquake',
                                 'Cyprus Peace Operation', 'Syrian Refugees'),
            notes = c('Only elections with non-swing result are considered.'))
```
